---
title: "Question1"
---
#First,
I want to see what causes difference among people’s health. The reason why some people live longer and better than others could be due to smoking, there are many papers on smoking and health.

Saha SP, Bhalla DK, Whayne TF, Gairola C. Cigarette smoke and adverse health effects: An overview of research trends and future needs. The International Journal of Angiology : Official Publication of the International College of Angiology, Inc. 2007;16(3):77-83.

research question 1: 
```{r}
Q1 <- brfss2013 %>% filter(!is.na(smoke100)) %>% filter(!is.na(genhlth))
ggplot(Q1, aes(genhlth, fill = smoke100))+geom_bar(position = "stack")

```
Clearly in the Excellent and Very Good health, people who don't smoke have greater proporotion. Whihc means smoking reduce the health.
Let's see the Chi square to test the relationship between the two varibles.
```{r}
attach(brfss2013)
chisq.test(genhlth,smoke100)
```

p-value is small, which indicates that smoking is siginificant related to the general health, which makes sense in real life, smoking leads to bad health.